CamIO data analysis

### 2020-08-04 R/ICCHP20.Rmd
Update renv + utils

if (!require(knitr)) install.packages("knitr")
if (!require(pacman)) install.packages("pacman")
pkg_list <- c("tidyverse", "glue", "magrittr", "plotly", "moments", "emmeans", "conflicted", "gridExtra", "kableExtra", "rcompanion", "broom", "rstatix", "ggpubr", "Rmisc")

pacman::p_load(char = pkg_list) #update=TRUE

knitr::opts_chunk$set(
  warning = FALSE,
  echo = FALSE,
  message = FALSE,
  error=FALSE,
  cache = FALSE
)

options(scipen=999, digits=4)

@@

>>>>

source("utils/dependencies.R", echo=F)

pkg_list <-
  c(
    "knitr",
    "tidyverse",
    "glue",
    "magrittr",
    "plotly",
    "moments",
    "emmeans",
    "conflicted",
    "gridExtra",
    "kableExtra",
    "rcompanion",
    "broom",
    "rstatix",
    "ggpubr",
    "Rmisc",
    "lme4"
  )

update_packages(pkg_list)

options(install.packages.check.source = "no", scipen=999, digits=4)

knitr::opts_chunk$set(
  warning = TRUE,
  echo = FALSE,
  message = TRUE,
  error = TRUE,
  cache = FALSE
)

@@

## Analysis tests:

```{r}
lme0 <- lmer(data = data.long, formula = Time ~ Condition + (1|Participant), REML=FALSE)
lme0 #%>% broom::tidy()
```

```{r}
lme1 <- lmer(data = data.long, formula = Time ~ (1|Participant), REML=FALSE)
lme1
```

```{r}
lme2 <- lmer(data = data.long, formula = Time ~ Condition + (Condition|Participant), REML=FALSE)
lme2
```

```{r}
AIC(lme0, lme1, lme2)
```

```{r}
anova(lme0, lme1)
```

### 2020-08-04 R/Index.Rmd
Update renv + utils

if (!require(knitr)) install.packages("knitr")
if (!require(pacman)) install.packages("pacman")
pkg_list <- c("tidyverse", "glue", "broom", "magrittr", "prettydoc", "DT", "reshape2", "plotly", "moments", "emmeans", "gtsummary", "lmtest", "table1", "rstatix", "lme4", "ggeffects", "conflicted", "forecast", "Rmisc", "gridExtra", "kableExtra", "rcompanion")

pacman::p_load(char = pkg_list) #update=TRUE
#pacman::p_load_gh(c("rstudio/gt", "tidyverse/dplyr"))
#knitr::write_bib(c(.packages(), pkg_list), 'bib/packages.bib')

>>>>

source("utils/dependencies.R", echo=F)

pkg_list <- c("tidyverse", "glue", "broom", "magrittr", "prettydoc", "DT", "reshape2", "plotly", "moments", "emmeans", "gtsummary", "lmtest", "table1", "rstatix", "lme4", "ggeffects", "conflicted", "forecast", "Rmisc", "gridExtra", "kableExtra", "rcompanion")

update_packages(pkg_list)
